Final Report Semester Project

### 2018-12-13 Visualizations/Draft Visualizations Template.Rmd
Corrected anon policies by company size visualization
X axis label was wrong

```{r}
dr1 <-as.data.frame(rowprop)
# Distribution of respondents among gender provided they may/have/donot have a mental diorder 
ggplot(data = dr1, aes(x =Var1 , y = Freq, fill = Var2)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
  labs(x = NULL, y = 'Proportion', fill = 'Gender')+ggtitle('Distribution of mental health status among genders (1)')
```

@@

```{r}
#Table : % of each level gender who may, don't or have mental disorder
colprop <- prop.table(gender_disorder,2)
colprop
```
```{r}
# Distribution of respondents who may/have/donot have a mental diorder over the gender
dr2 <-as.data.frame(colprop)
ggplot(data = dr2, aes(x =Var2 , y = Freq, fill = Var1)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
  labs(x = NULL, y = 'Proportion', fill = 'Disorder')+ggtitle('Distribution of mental health status among genders (2)')
```

@@

#Distribution of respondents reporting a mental disorder by age groups
ggplot(data = dfageprop, aes(x =Var2 , y = Freq, fill = Var1)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
  labs(x = "Age Groups", y = 'Proportion', fill = 'Disorder')+ggtitle('Distribution of mental health status based on age groups (1)')
```

@@

```{r}
dfageprop1 <- as.data.frame(ageprop1)
ggplot(data = dfageprop1, aes(x =Var1 , y = Freq, fill = Var2)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
  labs(x = "Disorder", y = 'Proportion', fill = 'Age group')+ggtitle('Distribution of mental health status based on age groups (2)')
```

@@

```{r}
#Create visualization
AnoymityPolicies_By_CompanySize_Viz <- ggplot(health, aes(x = health$AnonPolicies2))+geom_bar(fill="purple")+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Anonymity Protections by Comapny Size") + xlab("Perceived Difficulty Level") + ylab("Count")+ theme(axis.title=element_text(size=12))
AnoymityPolicies_By_CompanySize_Viz
```

@@

Shruti -

>>>>

```{r}
dr1 <-as.data.frame(rowprop)
# Distribution of respondents among gender provided they may/have/donot have a mental diorder 
ggplot(data = dr1, aes(x =Var1 , y = Freq, fill = Var2)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
  labs(x = NULL, y = 'Proportion', fill = 'Gender')+ggtitle('Distribution of mental health status among genders')
```

@@

```{r}
#Table : % of each level gender who may, don't or have mental disorder
colprop <- prop.table(gender_disorder,2)
colprop
```
```{r}
# Distribution of respondents who may/have/donot have a mental diorder over the gender
dr2 <-as.data.frame(colprop)
ggplot(data = dr2, aes(x =Var2 , y = Freq, fill = Var1)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
  labs(x = NULL, y = 'Proportion', fill = 'Disorder')+ggtitle('Distribution of mental health status among genders')
```

@@

#Distribution of respondents reporting a mental disorder by age groups
ggplot(data = dfageprop, aes(x =Var2 , y = Freq, fill = Var1)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
  labs(x = "Age Groups", y = 'Proportion', fill = 'Disorder')+ggtitle('Distribution of mental health status based on age groups')
```

@@

```{r}
dfageprop1 <- as.data.frame(ageprop1)
ggplot(data = dfageprop1, aes(x =Var1 , y = Freq, fill = Var2)) + 
  geom_bar(stat = 'identity', position = 'dodge', alpha = 2/3) +              
  labs(x = "Disorder", y = 'Proportion', fill = 'Age group')+ggtitle('Distribution of mental health status based on age groups')
```

@@

```{r}
#Create visualization
AnoymityPolicies_By_CompanySize_Viz <- ggplot(health, aes(x = health$AnonPolicies2))+geom_bar(fill="purple")+facet_wrap(~health$CompanySize, scales="free_y") + ggtitle("Anonymity Protections by Comapny Size") + xlab("Is your anonymity protected?") + ylab("Count")+ theme(axis.title=element_text(size=12))
AnoymityPolicies_By_CompanySize_Viz
```

@@

Shruti - Collaborated with the team members to decide upon work plan and the tasks. For data cleaning, I examined nine variables for any issues. Worked on the age variable where I replaced the meaningless ages like 3, 110 with the average age.  I exmained all the answers to the gender variable as they were subjective responses and divided them into Male, Female and others accordingly. For the descriptive analysis, I worked with the nine variables using summary and tables. For the visualization and plotting, I worked on the distribution of mental disorder. I analysed the responses to come up with a way to split it. For instance, the responses were of the format - Anxiety Disorder (Generalized, Social, Phobia, etc)|Mood Disorder (Depression, Bipolar Disorder, etc), I split them and separated them using R code to just the higher categories like anxiety Disorder, Mood Disorder to visualise it. For ease of visualisations using age, I created age groups (17-37, 37-57 etc). I visualised the distribution of mental illness across gender and age. I also did the visualisation and interpretations on negative consequences on discussing physical vs mental disorders. I documented my parts in the R markdown file. I worked on my parts for the presentation. For final package, I cleaned up the analaysis and visualizations that I worked on as well.
